---
title             : "Experiment 2 Analysis"
shorttitle        : "Revised Exp 2"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "doc"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE, warning=F, message=F}
library(here)

here::i_am('exp2_greetings/revised_ms_analyses.Rmd')
source(here('_libraries_functions_ggvars.R'))
source(here('exp2_greetings/read_in_data.R'))

set.seed(36)
knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed,
  echo=T,
  message=F,
  warning=F,
  digits=3)
```

## Experiment 2: Honorific Greetings  

### Participants  

```{r r2-g-pps}
g_fin <- read.csv(here('data/greetings_reviewer2_data.csv'))
g_fin$subject_id <- as.factor(g_fin$subject_id)

g_pp_tab <- g_fin %>% 
  distinct(subject_id, bebe_meses)%>% 
  summarize(min=min(bebe_meses),
            max=max(bebe_meses),
            M=mean(bebe_meses),
            SD=sd(bebe_meses))

G_N <- nrow(g_fin %>% 
  distinct(subject_id, bebe_meses))
G_MIN_AGE <- op(g_pp_tab$min)
G_MAX_AGE <- op(g_pp_tab$max)
G_MEAN_AGE <- op(g_pp_tab$M)
G_SD_AGE <- op(g_pp_tab$SD)
```

```{r r2-g-moms}
g_mama_tab <- demo %>%
  filter(subject_id %in% g_fin$subject_id,
         !is.na(mama_edad)) %>%
  summarize(min=min(mama_edad),
            max=max(mama_edad),
            M=mean(mama_edad),
            SD=sd(mama_edad))

G_MOT_MIN_AGE <- op(g_mama_tab$min)
G_MOT_MAX_AGE <- op(g_mama_tab$max)
G_MOT_M_AGE <- op(g_mama_tab$M)
G_MOT_SD_AGE <- op(g_mama_tab$SD)
```

We report on data from $`r G_N`$ infants (\textit{range}$=`r G_MIN_AGE`-`r G_MAX_AGE`$\textit{mos}, $M_\textnormal{age}=`r G_MEAN_AGE`$\textit{mos}, $SD_\textnormal{age}=`r G_SD_AGE`$\textit{mos}) tested in the Canada Chica \textit{paraje} of a Tseltal Maya community in Tenejapa, Chiapas, in Southern Mexico. 

Mothers ranged in age from $`r G_MOT_MIN_AGE`$ to $`r G_MOT_MAX_AGE`$\textit{yrs} ($M_\textnormal{age}=`r G_MOT_M_AGE`$\textit{yrs}, $SD_\textnormal{age}=`r G_MOT_SD_AGE`$\textit{yrs}) 

### Mean Difference Score Analysis  

```{r r2-g-diffs-df}
g_fin$stimulus_set <- ''

g_fin[g_fin$old_trial_name %in% c('old_woman-YOUNG_MAN',
                          'OLD_WOMAN-young_man'), ]$stimulus_set <- 'A'

g_fin[g_fin$old_trial_name %in% c('young_man-OLD_WOMAN',
                          'YOUNG_MAN-old_woman'), ]$stimulus_set <- 'B'

g_fin[g_fin$old_trial_name %in% c('old_man-YOUNG_WOMAN',
                          'OLD_MAN-young_woman'), ]$stimulus_set <- 'C'

g_fin[g_fin$old_trial_name %in% c('young_woman-OLD_MAN',
                          'YOUNG_WOMAN-old_man'), ]$stimulus_set <- 'D'

g_fin$target_stimulus <- paste(g_fin$target_noun, g_fin$stimulus_set, sep='')
g_fin$non_target_stimulus <- ''

g_fin[g_fin$target_stimulus=='young_manA',]$non_target_stimulus <- 'old_womanA'
g_fin[g_fin$target_stimulus=='old_womanA',]$non_target_stimulus <- 'young_manA'

g_fin[g_fin$target_stimulus=='young_manB',]$non_target_stimulus <- 'old_womanB'
g_fin[g_fin$target_stimulus=='old_womanB',]$non_target_stimulus <- 'young_manB'

g_fin[g_fin$target_stimulus=='young_womanC',]$non_target_stimulus <- 'old_manC'
g_fin[g_fin$target_stimulus=='old_manC',]$non_target_stimulus <- 'young_womanC'

g_fin[g_fin$target_stimulus=='young_womanD',]$non_target_stimulus <- 'old_manD'
g_fin[g_fin$target_stimulus=='old_manD',]$non_target_stimulus <- 'young_womanD'

g_target_df <- g_fin %>%
  filter(noun_pair %in% c('old_man-young_woman', 'old_woman-young_man'),
         subject_id %in% g_subjects) %>%
  dplyr::select(subject_id, 
                bebe_meses,
                age_centered,
                age_group,
                stimulus_set, 
                target_stimulus, 
                noun_pair, 
                post1_target_prop) %>%
  mutate(merge_on_noun = target_stimulus)

g_non_target_df <- g_fin %>%
  filter(noun_pair %in% c('old_man-young_woman', 'old_woman-young_man'),
                          subject_id %in% g_subjects) %>%
  dplyr::select(subject_id, 
                bebe_meses,
                age_centered,
                age_group,
                noun_pair,
                stimulus_set, 
                non_target_stimulus,
                post1_nontarget_prop) %>%
  mutate(merge_on_noun=non_target_stimulus)

g_target_nontarget_props_df <- merge(g_target_df, g_non_target_df, 
                                      by=c('subject_id', 
                                           'noun_pair',
                                           'stimulus_set',
                                           'merge_on_noun',
                                           'age_centered',
                                           'bebe_meses',
                                           'age_group'), all=T) %>%
  group_by(subject_id, bebe_meses, age_centered, age_group,
           noun_pair, stimulus_set, merge_on_noun) %>%
  summarize(post1_target_prop = na.mean(post1_target_prop),
            post1_nontarget_prop = na.mean(post1_nontarget_prop))

g_diffs_df <-  g_target_nontarget_props_df %>%
  dplyr::select(subject_id, bebe_meses, age_centered, age_group,
                noun_pair, stimulus_set, merge_on_noun, 
                post1_target_prop,
                post1_nontarget_prop) %>%
  mutate(diff = post1_target_prop - post1_nontarget_prop) %>%
  group_by(subject_id, 
           bebe_meses, age_centered, age_group, 
           noun_pair, stimulus_set) %>%
  summarize(stim_pair_diff = mean(diff)) %>%
  group_by(subject_id, bebe_meses, age_centered, age_group, noun_pair) %>%
  summarize(noun_pair_diff = na.mean(stim_pair_diff)) %>%
         filter(!is.na(noun_pair))

g_diffs_df$age_std <- g_diffs_df$age_centered/as.numeric(G_SD_AGE)

write.csv(g_diffs_df,
         here('data/r_analysis_dfs', 'g_bs2012_diffs.csv')
         )
```

#### By Item  

```{r r2-g-by-item-overall}
set.seed(36)

g_by_item_tab <- g_diffs_df %>% 
  group_by(noun_pair, subject_id, age_centered) %>%
  summarize(subj_item_mean = na.mean(noun_pair_diff)) %>%
  filter(!is.na(subj_item_mean)) %>%
  ungroup() %>%
  group_by(noun_pair) %>%
  summarize(n = n(),
            M = na.mean(subj_item_mean),
            cil=M-ci.low(subj_item_mean),
            cih = M+ci.high(subj_item_mean),
            min=min(subj_item_mean, na.rm=T),
            max=max(subj_item_mean, na.rm=T))

G_ALL_ITEM_MEAN <- mean(g_by_item_tab$M)
G_ALL_ITEM_CIL <- G_ALL_ITEM_MEAN - ci.low(g_by_item_tab$M)
G_ALL_ITEM_CIH <- G_ALL_ITEM_MEAN + ci.high(g_by_item_tab$M)
G_ALL_ITEM_MIN <- min(g_by_item_tab$M)
G_ALL_ITEM_MAX <- max(g_by_item_tab$M)
N_G_POSITIVE_ITEMS <- sum(g_by_item_tab$M > 0)
```

```{r r2-g-by-item-table-s2}
set.seed(36)

write(apa_table(g_by_item_tab, 
                caption='Experiment 2 Item Means'),
      here('supplement/tables/exp_2/g_by_item_tab.tex'))

xtable2kable(g_by_item_tab)
```

#### Non-parametric  

```{r r2-g-item-bayes}
# Bayes factor
ttestBF(g_by_item_tab$M)
```

```{r r2-g-item-d}
# Standard deviation
stdev=sd(g_by_item_tab$M, na.rm=T)
# Mean
mean_data=na.mean(g_by_item_tab$M)
# Effect size
G_ITEM_D=abs(mean_data/stdev)
```

```{r r2-g-item-wilcox}
g_by_item_sub_tab <- g_diffs_df %>% 
  group_by(noun_pair, subject_id) %>%
  summarize(subj_item_mean = na.mean(noun_pair_diff)) %>%
  ungroup() %>%
  filter(!is.na(subj_item_mean)) 

g_item_wilcox <- wilcox.test(g_by_item_sub_tab$subj_item_mean,
                             mu=0, 
                             alternative="two.sided")

G_ITEM_P_WILCOX <- reportP(as.numeric(g_item_wilcox['p.value']))
```

```{r r2-cn-item-binom}
g_item_binom <- binom.test(2, 2, p=.5)

G_ITEM_P_BINOM <- reportP(g_item_binom$p.value)
```

```{r r2-g-by-item-plots}
set.seed(36)

g_diffs_df$noun_pair_label <- ''
g_diffs_df[
  g_diffs_df$noun_pair=='old_woman-young_man',]$noun_pair_label <-
  'old woman -\nyoung man'
g_diffs_df[
  g_diffs_df$noun_pair=='old_man-young_woman',]$noun_pair_label <-
  'old man -\nyoung woman'

g_plot2 <- g_diffs_df %>% 
  group_by(noun_pair, noun_pair_label, subject_id) %>%
  summarize(subj_item_mean = na.mean(noun_pair_diff)) %>%
  ungroup() %>%
  filter(!is.na(subj_item_mean)) %>%
  group_by(noun_pair, noun_pair_label) %>%
  mutate(n = n(),
            item_mean = na.mean(subj_item_mean),
            min=min(subj_item_mean, na.rm=T),
            max=max(subj_item_mean, na.rm=T),
            ci.low=item_mean-ci.low(subj_item_mean),
            ci.high = item_mean+ci.high(subj_item_mean)) %>%
  ggplot(., aes(x=noun_pair_label, y=item_mean, color=noun_pair)) +
    geom_hline(yintercept=0) +
  geom_jitter(aes(y=subj_item_mean), alpha=.5) +
  geom_pointrange(aes(y=item_mean, ymin=ci.low, ymax=ci.high, 
                      fill=noun_pair), shape=23, size=.5) + 
  sb.density.theme +
  theme(axis.text.x = element_text(angle=60, vjust=1, hjust=1, size=10),
        legend.position = "none",
        axis.title = element_text(colour="gray30", size=11, face="bold")) +
  ylab("Increase in Target Looking") +
  xlab("Honorific-Pair") +
  ylim(-1, 1) + 
  scale_discrete_manual(aesthetics=c("color", "fill"), 
                        values=greeting_pair_fills)
```

#### By Subject 

```{r r2-g-by-sub-tab}
set.seed(36)

g_sub_df <- g_diffs_df %>% 
  filter(!is.na(noun_pair_diff)) %>%
  group_by(subject_id, bebe_meses, age_centered) %>%
  summarize(g_M = na.mean(noun_pair_diff),
            n=n()) 

G_N_FOR_MEAN_DIFF_ANALYSES <- nrow(g_sub_df)

g_positive_scorers_age_tab <- g_sub_df %>%
  filter(g_M>0) %>%
  ungroup() %>%
  summarize(mean=mean(bebe_meses),
            sd=sd(bebe_meses),
            ci.low=mean-ci.low(bebe_meses),
            ci.high=mean+ci.high(bebe_meses))

G_N_POSITIVE_SUBS <- sum(g_sub_df$g_M>0)
G_N_TOTAL_SUBS <- nrow(g_sub_df)
G_PS_MEAN_AGE <- g_positive_scorers_age_tab$mean
G_PS_CILO_AGE <- g_positive_scorers_age_tab$ci.low
G_PS_CIHI_AGE <- g_positive_scorers_age_tab$ci.high
G_PS_SD_AGE <- g_positive_scorers_age_tab$sd
```

```{r r2-g-by-subject-overall-mean}
set.seed(36)

 g_by_sub_overall_tab <- g_diffs_df %>%
  group_by(subject_id) %>%
  summarize(subj_mean = na.mean(noun_pair_diff)) %>%
  ungroup() %>%
  filter(!is.na(subj_mean)) %>%
  summarize(group_subject_mean = mean(subj_mean),
            min=min(subj_mean),
            max=max(subj_mean),
            ci.low=group_subject_mean-ci.low(subj_mean),
            ci.high = group_subject_mean+ci.high(subj_mean))

G_ALL_SUB_MEAN <- g_by_sub_overall_tab$group_subject_mean
G_ALL_SUB_CIL <- g_by_sub_overall_tab$ci.low
G_ALL_SUB_CIH <- g_by_sub_overall_tab$ci.high
G_ALL_SUB_MIN <- g_by_sub_overall_tab$min
G_ALL_SUB_MAX <- g_by_sub_overall_tab$max
```

```{r r2-g-by-subject-plot, fig.align='center', fig.width=6}

g_diffs_df %>% 
  filter(!is.na(noun_pair_diff)) %>%
  group_by(subject_id, bebe_meses) %>%
  summarize(subj_item_mean = na.mean(noun_pair_diff),
            n_items = n()) %>%
  mutate(all_pairs = n_items==2) %>%
  filter(!is.na(subj_item_mean)) %>%
ggplot(.) +
  geom_point(aes(x=bebe_meses, y=subj_item_mean), 
             color=rf_color, fill=rf_fill, 
             shape=24, size=2.5) + 
  geom_linerange(aes(x=bebe_meses, ymin=0, ymax=subj_item_mean),
                 color=rf_color) +
  geom_hline(yintercept=0) +
  sb.density.theme +
  theme(
    axis.title = element_text(colour="gray30", size=11, face="bold"),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30")) +
  ylab("Increase in Target Looking") +
  xlab("Child Age (months)") +
  xlim(4.5, 16.0) +
  scale_x_continuous(breaks=c(4,5,6,7,8,9,10,11,12,13,14,15)) +
  ylim(-.4, .6) 

ggsave(here('supplement/plots/exp_2/pdfs', 'g_meandiffs_bysub.pdf'),
       device='pdf', width=2.5, height=1.5, units='in', scale=2)
ggsave(here('supplement/plots/exp_2/pngs', 'g_meandiffs_bysub.png'), 
       device='png', width=2.5, height=1.5, units='in', scale=2)
```

#### Non-parametric 

```{r r2-g-bayes}
# Bayes factor
ttestBF(g_sub_df$g_M)
```

```{r r2-g-d}
# Standard deviation
stdev=sd(g_sub_df$g_M)
# Mean
mean_data=mean(g_sub_df$g_M)
# Effect size
G_SUBJ_D=abs(mean_data/stdev)
```

```{r g-subj-wilcox}
g_subj_wilcox <- wilcox.test(g_sub_df$g_M, mu=0, 
                              alternative="two.sided")

G_SUBJ_P_WILCOX <- reportP(g_subj_wilcox$p.value)
```

```{r g-subj-binom}
g_subj_binom <- binom.test(G_N_POSITIVE_SUBS, G_N_FOR_MEAN_DIFF_ANALYSES, p=.5)
G_SUBJ_P_BINOM <- reportP(g_subj_binom$p.value)
```

#### MLM Intercept 

```{r r2-g-lmer}
set.seed(36)

g_model0 <- lmer(noun_pair_diff ~ 0 + (1|subject_id), REML = FALSE,
             g_diffs_df)
g_model1 <- lmer(noun_pair_diff ~ 1 + (1|subject_id), REML = FALSE,
               g_diffs_df)

g_b0_anova <- anova(g_model1, g_model0)
G_B0_CHISQ <- g_b0_anova$Chisq[2]
G_B0_P <- reportP(g_b0_anova$`Pr(>Chisq)`[2])

g_all_subs_intercept <- as.data.frame(
  cbind(b=fixef(g_model1),
  ci.low=confint(g_model1)[3,1], 
  ci.high=confint(g_model1)[3,2])
  )

G_B0_EST <- op(g_all_subs_intercept$b)
G_B0_CIL <- op(g_all_subs_intercept$ci.low)
G_B0_CIH <- op(g_all_subs_intercept$ci.high)

G_B0_TT_DF <- op(as.numeric(unlist(summary(g_model1)['coefficients'])[3]))
G_B0_TT_STAT <- op(as.numeric(
  unlist(summary(g_model1)['coefficients'])[4])
  )
G_B0_TT_P <- reportP(as.numeric(
  unlist(summary(g_model1)['coefficients'])[5])
  )

#noun pair not enough variance to warrant random intercept
write(texreg(g_model1), 
      file=here('supplement/tables/exp_2/g_lmer0_tab.tex'))
```

$`r N_G_POSITIVE_ITEMS`$/2 honorific-pairs showed positive mean difference scores. 
The mean across items was positive (\textit{range}: $`r G_ALL_ITEM_MIN`-`r G_ALL_ITEM_MAX`$, 
$M=`r G_ALL_ITEM_MEAN`$ [$`r G_ALL_ITEM_CIL`$, $`r G_ALL_ITEM_CIH`$]; $`r G_ITEM_P_WILCOX`$, Wilcoxon test; $`r G_ITEM_P_BINOM`$, binomial test; $d=`r G_ITEM_D`$).

$`r G_N_POSITIVE_SUBS`$/$`r G_N_TOTAL_SUBS`$ subjects showed a positive mean difference score ($M_\textnormal{age}=`r G_PS_MEAN_AGE`$ [$`r G_PS_CILO_AGE`$, $`r G_PS_CIHI_AGE`$], $SD_{age}=`r G_PS_SD_AGE`$). 
The mean across subjects was positive (\textit{range}: $`r G_ALL_SUB_MIN`-`r G_ALL_SUB_MAX`$, $M=`r G_ALL_SUB_MEAN`$ [$`r G_ALL_SUB_CIL`$, $`r G_ALL_SUB_CIH`$]; $`r G_SUBJ_P_WILCOX`$, Wilcoxon test, $`r G_SUBJ_P_BINOM`$, binomial test, $d=`r G_SUBJ_D`$).

A linear mixed effects model suggested that infants' positive mean performance was reliable, accounting for subject- and item-level variability ($\beta_0=`r G_B0_EST`$, 
\textit{95\% CI:} [$`r G_B0_CIL`$, $`r G_B0_CIH`$], 
$t(`r G_B0_TT_DF`)=`r G_B0_TT_STAT`$, 
$`r G_B0_TT_P`$, $\chi^2(1)=`r G_B0_CHISQ`$, $`r G_B0_P`$). 

#### Correlation with Age  

```{r r2-g-by-subject-age}
set.seed(36)

g_by_subj_age_tab <- g_diffs_df %>% 
  filter(!is.na(noun_pair_diff)) %>% 
  group_by(subject_id, bebe_meses, age_centered) %>%
  summarize(subj_item_mean = na.mean(noun_pair_diff),
            n_subjects = n(),
            min = min(noun_pair_diff, na.rm=T),
            max = max(noun_pair_diff, na.rm=T),
            ci.low = subj_item_mean-ci.low(noun_pair_diff),
            ci.high = subj_item_mean+ci.high(noun_pair_diff)) 

g_age_cor_test <- cor.test(g_by_subj_age_tab$bebe_meses, 
                           g_by_subj_age_tab$subj_item_mean,
                           method="kendall")

G_AGE_CORR <- as.numeric(g_age_cor_test$estimate)
G_AGE_CORR_P <- g_age_cor_test$p.value
G_AGE_CORR_T <- g_age_cor_test$statistic
```

Mean scores were not significantly correlated with infants' ages in months ($\tau=`r G_AGE_CORR`$, $p=`r G_AGE_CORR_P`$).

```{r r2-g-lm-age}
g_age_lm  <- lm(subj_item_mean ~ 1 + age_centered, g_by_subj_age_tab)
summary(g_age_lm)

write(texreg(g_age_lm), 
      file=here('supplement/tables/exp_2/g_age_lm_tab.tex')) 
```

### Pre/Post Looking Logit Model 

```{r r2-g-prepost-df}
g_supp_pre <- g_fin %>%
  select(pre_target_sum_ms, pre_nontarget_sum_ms, 
         subject_id, bebe_meses, age_centered, noun_pair, path) 

g_supp_pre$phase <- "pre-naming"
g_supp_pre$target_bins <- round(g_supp_pre$pre_target_sum_ms/20,0)
g_supp_pre$nontarget_bins <- round(g_supp_pre$pre_nontarget_sum_ms/20, 0)

g_supp_pre <- g_supp_pre %>% 
  select(subject_id, bebe_meses, age_centered, noun_pair, phase, 
         target_bins, nontarget_bins, path) 

g_supp_post <- g_fin %>% 
  select(post1_target_sum_ms, post1_nontarget_sum_ms, 
         subject_id, bebe_meses, age_centered, noun_pair, path) 

g_supp_post$phase <- "post-naming"
g_supp_post$target_bins <- round(g_supp_post$post1_target_sum_ms/20, 0)
g_supp_post$nontarget_bins <- round(g_supp_post$post1_nontarget_sum_ms/20, 0)

g_supp_post <- g_supp_post %>% 
  select(subject_id, bebe_meses, age_centered, noun_pair, phase, 
         target_bins, nontarget_bins, path) 

g_supp_stacked_r2 <- rbind(g_supp_pre, g_supp_post)

g_supp_stacked_r2$phase <- as.factor(g_supp_stacked_r2$phase)
g_supp_stacked_r2$phase <- relevel(g_supp_stacked_r2$phase, ref="pre-naming")
  
g_supp_stacked_r2 %>%
  group_by(subject_id, bebe_meses, age_centered, noun_pair, phase, path) %>%
  summarize(target_bins = target_bins, 
            nontarget_bins = nontarget_bins) %>%
  write.csv(., here('data/r_analysis_dfs', 
                  'g_prepost_target_looking.csv')
          )
```

_Get back to 126 trials_

```{r g-prepost-glmers, cache=T}
set.seed(36) 

g_supp_glmer_null <- glmer(cbind(target_bins, nontarget_bins) ~
                         1 + (1|subject_id),
                        family=binomial, g_supp_stacked_r2,
                        control=glmerControl(optimizer="bobyqa", 
                        optCtrl=list(maxfun=100000)))

g_supp_glmer <- glmer(cbind(target_bins, nontarget_bins) ~
                         phase + (1|subject_id),
                        family=binomial, g_supp_stacked_r2,
                        control=glmerControl(optimizer="bobyqa", 
                        optCtrl=list(maxfun=100000)))

g_supp_glmer_tab <- as.data.frame(
  cbind("OR"=op(exp(fixef(g_supp_glmer))),
        "CIL"=op(exp(confint.merMod(g_supp_glmer))[2:3,1]),
        "CIH"=op(exp(confint.merMod(g_supp_glmer))[2:3,2])))

G_POSTNAMING_OR <- g_supp_glmer_tab$OR[2]
G_POSTNAMING_CIL <- g_supp_glmer_tab$CIL[2]
G_POSTNAMING_CIH <- g_supp_glmer_tab$CIH[2]
G_PHASE_WALD_CHISQ <- Anova(g_supp_glmer)['phase','Chisq']
G_PHASE_WALD_P <- reportP(
  Anova(g_supp_glmer)['phase','Pr(>Chisq)'])
  
g_supp_age_glmer <- glmer(cbind(target_bins, nontarget_bins) ~
                         phase + age_centered + 
                           (1|subject_id),
                         family=binomial, g_supp_stacked_r2,
                        control=glmerControl(optimizer="bobyqa", 
                        optCtrl=list(maxfun=100000)))

summary(g_supp_glmer)
exp(fixef(g_supp_glmer))
exp(confint(g_supp_glmer))
Anova(g_supp_glmer)

#G_POSTNAMING_OR <- op(g_pp_age_glmer_tab$OR[2])
#G_POSTNAMING_CIL <- op(g_pp_age_glmer_tab$CIL[2])
#G_POSTNAMING_CIH <- op(g_pp_age_glmer_tab$CIH[2])
#G_PHASE_WALD_CHISQ <- op(Anova(g_supp_age_glmer)['phase','Chisq'])
#G_PHASE_WALD_P <- op(Anova(g_supp_age_glmer)['phase','Pr(>Chisq)'])

g_supp_ageint_glmer <- glmer(cbind(target_bins, nontarget_bins) ~
                         phase*age_centered + 
                           (1|subject_id), 
                        family=binomial, g_supp_stacked_r2)

confint.merMod(object = g_supp_ageint_glmer, method = "boot")

g_supp_ageint_glmer_tab <- as.data.frame(
  cbind("OR"=op(exp(fixef(g_supp_ageint_glmer))),
        "CIL"=op(exp(confint.merMod(object = g_supp_ageint_glmer, 
                                    method = "boot"))[2:5,1]),
        "CIH"=op(exp(confint.merMod(object = g_supp_ageint_glmer, 
                                    method = "boot"))[2:5,2])))

g_supp_ageint_anova <- anova(g_supp_glmer, g_supp_age_glmer,
                             g_supp_ageint_glmer)

G_POST_AGE_INT_PHASE_OR <- g_supp_ageint_glmer_tab$OR[2]
G_POST_AGE_INT_PHASE_CIL <- g_supp_ageint_glmer_tab$CIL[2]
G_POST_AGE_INT_PHASE_CIH <- g_supp_ageint_glmer_tab$CIH[2]
G_POST_AGE_INT_PHASE_WALD_CHISQ <- 
  Anova(g_supp_ageint_glmer)['phase','Chisq']
G_POST_AGE_INT_PHASE_WALD_P <-
  reportP(Anova(g_supp_ageint_glmer)['phase','Pr(>Chisq)'])

G_POST_AGE_INT_OR <- g_supp_ageint_glmer_tab$OR[4]
G_POST_AGE_INT_CIL <- g_supp_ageint_glmer_tab$CIL[4]
G_POST_AGE_INT_CIH <- g_supp_ageint_glmer_tab$CIH[4]
G_POST_AGE_INT_WALD_CHISQ <- 
  op(Anova(g_supp_ageint_glmer)['phase:age_centered','Chisq'])
G_POST_AGE_INT_WALD_P <-
  reportP(Anova(g_supp_ageint_glmer)['phase:age_centered','Pr(>Chisq)'])

G_POST_AGE_INT_DF <- g_supp_ageint_anova$Df[2]
G_POST_AGE_INT_CHISQ <- g_supp_ageint_anova$Chisq[2]
G_POST_AGE_INT_P <- reportP(g_supp_ageint_anova$`Pr(>Chisq)`[2])

Anova(g_supp_ageint_glmer)
  
write(texreg(list(g_supp_glmer, g_supp_age_glmer)), 
      here('supplement/tables/exp_2', 'g_prepost_glmers_w_wo_age_tab.tex')
      )

write(texreg(list(g_supp_glmer, g_supp_age_glmer, g_supp_ageint_glmer)),
      here('supplement/tables/exp_2', 'g_prepost_3glmers_tab.tex')
      )
```

## Results Text  

The odds ratio for trial phase (\textsc{post-naming} OR$=`r G_POSTNAMING_OR`$, \textit{95\% CI:} [$`r G_POSTNAMING_CIL`$, $`r G_POSTNAMING_CIH`$]) suggests that infants' relative looking time to the competitor faces was responsive to the honorific term used by their caregivers: infants dedicated a significantly greater proportion of their looking time to the target face after hearing the honorific ($Wald \chi^2(1)=`r G_PHASE_WALD_CHISQ`$, $`r G_PHASE_WALD_P`$, \textit{Cohen} $d=0.65$).

As in Experiment 1, a model which additionally included infant age and its interaction with trial phase resulted in a significantly better fit ($\chi^2(`r G_POST_AGE_INT_DF`)=`r G_POST_AGE_INT_CHISQ`$, $`r G_POST_AGE_INT_P`$), showing a reliable effect of trial phase ($OR=`r G_POST_AGE_INT_PHASE_OR`$, \textit{95\% CI:} [$`r G_POST_AGE_INT_PHASE_CIL`$, $`r G_POST_AGE_INT_PHASE_CIH`$], \textit{Wald} $\chi^2(1)=`r G_POST_AGE_INT_PHASE_WALD_CHISQ`$, $`r G_POST_AGE_INT_PHASE_WALD_P`$, \textit{Cohen} $d=0.65$) and interaction with age, such that older children showed a greater increase in the ratio of target:non-target looking after hearing the target word ($OR=`r G_POST_AGE_INT_OR`$, \textit{95\% CI:} [$`r G_POST_AGE_INT_CIL`$, $`r G_POST_AGE_INT_CIH`$], $Wald \chi^2(1)=`r G_POST_AGE_INT_WALD_CHISQ`$, $`r G_POST_AGE_INT_WALD_P`$, \textit{Cohen} $d=0.081$).

#### GLMERs by Age Group 

From B&S2012:  
>A separate hierarchical logistic regression model was created
for each group of children (6–9 mo, 10–13 mo, 14–16 mo, and 18–
20 mo) for each trial type (paired-picture and scene). Phase of
trial (pretarget utterance vs. posttarget utterance) was included
as a fixed-effect predictor, and subject and item were included
as random effects. Each model predicts (the log of) the ratio of
target to distracter looking, as calculated by counting time bins.

# Trial Counts Across Analyses

```{r r2-g-trials-lost}
G_TOTAL_TRIALS_N <- nrow(g_fin)

G_MEAN_DIFF_TRIALS_N <- g_target_nontarget_props_df %>%
  dplyr::select(subject_id, age_centered, 
                noun_pair, stimulus_set, merge_on_noun, 
                post1_target_prop,
                post1_nontarget_prop) %>%
  mutate(diff = post1_target_prop - post1_nontarget_prop) %>%
  group_by(
    subject_id, age_centered, noun_pair, stimulus_set
  ) %>%
  summarize(stim_pair_diff = mean(diff)) %>%
  filter(!is.na(stim_pair_diff)) %>%
  nrow(.) * 2

G_DROPPED_TRIALS <- G_TOTAL_TRIALS_N - G_MEAN_DIFF_TRIALS_N 
G_DROPPED_TRIAL_PERCENT <- G_DROPPED_TRIALS/G_TOTAL_TRIALS_N
```

`r G_DROPPED_TRIALS` trials dropped for paired difference score analysis, or `r G_DROPPED_TRIAL_PERCENT*100`\% of non-excluded trials. 

```{r r2-g-trials-summary}
g_supp_stacked_r2 %>%
  group_by(subject_id) %>%
  summarize(trials=n()/2) %>%
  ungroup() %>%
  summarize(min=min(trials),
            max=max(trials),
            mean=mean(trials),
            med=median(trials),
            mode=DescTools::Mode(trials))
```

# Trial Durations  

```{r r2-g-durations-trial}
G_MED_TRIAL_DUR_S <- median(g_fin$trialtolookingoffset_dur_s, na.rm=T)
G_MIN_TRIAL_DUR_S <- min(g_fin[g_fin$trial_dur_s<30,]$trialtolookingoffset_dur_s)
G_MAX_TRIAL_DUR_S <- max(g_fin[g_fin$trial_dur_s<30,]$trialtolookingoffset_dur_s)
G_MEAN_TRIAL_DUR_S <- mean(
  g_fin[g_fin$trial_dur_s<30,]$trialtolookingoffset_dur_s)
G_CIL_TRIAL_DUR_S <- G_MEAN_TRIAL_DUR_S - ci.low(
  g_fin[g_fin$trial_dur_s<30,]$trialtolookingoffset_dur_s)
G_CIH_TRIAL_DUR_S <- G_MEAN_TRIAL_DUR_S + ci.high(
  g_fin[g_fin$trial_dur_s<30,]$trialtolookingoffset_dur_s)

ggplot(g_fin, aes(x=trialtolookingoffset_dur_s)) +
  geom_histogram(fill="#bae4bc") +
  sb.density.theme +
  geom_vline(xintercept=G_MED_TRIAL_DUR_S, color="red", lty=2) +
  xlim(6,22) +
  xlab("Trial Duration (s)") +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank() ,
        panel.grid.major = element_blank() ,
        panel.grid.minor = element_blank() ,
        panel.border = element_blank() ,
        panel.background = element_blank(),
        axis.line = element_line(color = "gray30")) +
  annotate(
    "text", label = "Median = 14s",
    x = G_MED_TRIAL_DUR_S+2, y = 16, size = 4, colour = "red")

ggsave(here('supplement/plots/exp_2/pdfs', 'g_trialdur_histogram.pdf'), 
       device='pdf', width=2.5, height=1.25, units='in', scale=2.5)
ggsave(here('supplement/plots/exp_2/pngs', 'g_trialdur_histogram.png'),
       device='png', width=2.5, height=1.25, units='in', scale=2.5)
```

```{r r2-g-durations-triallooking}

G_MED_TRIAL_LOOKING_S <- median(
  g_fin$totaltrialtime_looking_sum_s)
G_MIN_TRIAL_LOOKING_S <- 
  min(g_fin$totaltrialtime_looking_sum_s)
G_MAX_TRIAL_LOOKING_S <- 
  max(g_fin$totaltrialtime_looking_sum_s)
G_MEAN_TRIAL_LOOKING_S <- 
  mean(g_fin$totaltrialtime_looking_sum_s)
G_CIL_TRIAL_LOOKING_S <- G_MEAN_TRIAL_LOOKING_S - 
  ci.low(g_fin$totaltrialtime_looking_sum_s)
G_CIH_TRIAL_LOOKING_S <- G_MEAN_TRIAL_LOOKING_S + 
  ci.high(g_fin$totaltrialtime_looking_sum_s)

ggplot(g_fin, aes(x=totaltrialtime_looking_sum_s)) +
  geom_histogram(fill="#7bccc4") +
  sb.density.theme +
  geom_vline(xintercept=G_MED_TRIAL_LOOKING_S, 
             color="red", lty=2) +
  xlim(2,20) +
  xlab("Total Looking Time Duration (s)") +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color = "gray30"))  +
  annotate(
    "text", label = "Median = 12s",
    x = G_MED_TRIAL_LOOKING_S+2.5, y = 12, size = 4, colour = "red")

ggsave(here('supplement/plots/exp_2/pdfs', 'g_lookingtime_histogram.pdf'), 
       device='pdf', width=2.5, height=1.25, units='in', scale=2.5)
ggsave(here('supplement/plots/exp_2/pngs', 'g_lookingtime_histogram.png'),
       device='png', width=2.5, height=1.25, units='in', scale=2.5)
```

```{r r2-g-durs-lookingprop}

G_MED_LOOKING_PROP <- median(
  g_fin$trialtolookingoffset_prop)
G_MIN_LOOKING_PROP <- min(
  g_fin$trialtolookingoffset_prop)
G_MAX_LOOKING_PROP <- max(
  g_fin$trialtolookingoffset_prop)
G_MEAN_LOOKING_PROP <- mean(
  g_fin$trialtolookingoffset_prop)
G_CIL_LOOKING_PROP <- G_MEAN_LOOKING_PROP - 
  ci.low(g_fin$trialtolookingoffset_prop)
G_CIH_LOOKING_PROP <- G_MEAN_LOOKING_PROP + 
  ci.high(g_fin$trialtolookingoffset_prop)

ggplot(g_fin, aes(x=trialtolookingoffset_prop)) +
  geom_histogram(fill="#7bccc4") +
  sb.density.theme +
  geom_vline(xintercept=G_MED_LOOKING_PROP, color="red", lty=2) +
  xlim(0,1) +
  xlab("Overall Looking Time Proportion") +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank() ,
        panel.grid.major = element_blank() ,
        panel.grid.minor = element_blank() ,
        panel.border = element_blank() ,
        panel.background = element_blank(),
        axis.line = element_line(color = "gray30")) +
  annotate(
    "text", label = "Median = 0.85",
    x = G_MED_LOOKING_PROP-.12, y = 16, size = 4, colour = "red")

ggsave(here('supplement/plots/exp_2/pdfs', 'g_lookingprop_histogram.pdf'), 
       device='pdf', width=2.5, height=1.25, units='in', scale=2.5)
ggsave(here('supplement/plots/exp_2/pngs', 'g_lookingprop_histogram.png'),
       device='png', width=2.5, height=1.25, units='in', scale=2.5)
```

```{r r2-g-pre-duration}

G_MED_PRE_DUR_S <- median(g_fin$pre_dur_ms/1000)
G_MIN_PRE_DUR_S <- min(g_fin$pre_dur_ms/1000)
G_MAX_PRE_DUR_S <- max(g_fin[g_fin$pre_dur_ms<10000,]$pre_dur_ms/1000)
G_MEAN_PRE_DUR_S <- mean(g_fin[g_fin$pre_dur_ms<10000,]$pre_dur_ms/1000)

ggplot(g_fin, aes(x=pre_dur_ms/1000))+
  geom_histogram(fill="#bae4bc") +
  sb.density.theme +
  geom_vline(xintercept=G_MED_PRE_DUR_S, color="red", lty=2) +
  xlim(2,6.5)+
  xlab('"Pre-Naming" Window Duration (s)') +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank() ,
        panel.grid.major = element_blank() ,
        panel.grid.minor = element_blank() ,
        panel.border = element_blank() ,
        panel.background = element_blank(),
        axis.line = element_line(color = "gray30")) +
  annotate(
    "text", label = "Median = 3.5s",
    x = G_MED_PRE_DUR_S+2.4, y = 25, size = 4, colour = "red")
```

```{r r2-cn-durs-prepost-lookingdurs}
g_prelookingdur_df <- g_fin %>% 
  mutate(window = '"Pre-Naming" Window',
         looking_dur = pre_looking_sum_ms/1000,
         median = median(looking_dur),
         mean = mean(looking_dur)) %>%
  dplyr::select("subject_id", "window", "looking_dur", "median", "mean")

G_PRE_MIN_DUR <- min(g_prelookingdur_df$looking_dur)
G_PRE_MAX_DUR <- max(g_prelookingdur_df$looking_dur)
G_PRE_MEAN_DUR <- mean(g_prelookingdur_df$looking_dur)
G_PRE_MEDIAN_DUR <- median(g_prelookingdur_df$looking_dur)

g_postlookingdur_df <- g_fin %>% 
  mutate(window = '"Post-Naming"/Analysis Window',
         looking_dur = post1_looking_sum_ms/1000,
         median = median(looking_dur),
         mean = mean(looking_dur)) %>%
  dplyr::select("subject_id", "window", "looking_dur", "median", "mean")

G_POST_MIN_DUR <- min(g_postlookingdur_df$looking_dur)
G_POST_MAX_DUR <- max(g_postlookingdur_df$looking_dur)
G_POST_MEAN_DUR <- mean(g_postlookingdur_df$looking_dur)
G_POST_MEDIAN_DUR <- median(g_postlookingdur_df$looking_dur)

g_prepost_lookingdur_df <- rbind(g_prelookingdur_df, g_postlookingdur_df)
g_prepost_lookingdur_df$window <- 
  factor(g_prepost_lookingdur_df$window, levels=c(
    '"Pre-Naming" Window','"Post-Naming"/Analysis Window'), ordered=T) 

g_prepost_lookingdur_label_df <- g_prepost_lookingdur_df %>%
  group_by(window) %>%
  summarize(median=median(median),
            label=paste("Median =", round(median, 2), sep=" "))

g_pp_durs <- ggplot(g_prepost_lookingdur_df, aes(x=looking_dur)) +
  geom_histogram(fill="#7bccc4") +
  sb.density.theme +
  geom_vline(aes(xintercept=median), color="red", lty=2) +
  xlim(0,5) +
  xlab("Looking Time Duration (s)") +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank(),
        strip.text.x = element_text(colour="gray30", size=11))+
  facet_wrap(~window) +
  geom_text(data=g_prepost_lookingdur_label_df,
            aes(x=median-1.2, label=label), y=45, 
            color="red", size=4)

ggsave(here('supplement/plots/exp_2/pdfs', 'g_lookingdurs_prepost.pdf'), 
       device='pdf', width=2.75, height=1.5, units='in', scale=2.5)
ggsave(here('supplement/plots/exp_2/pngs', 'g_lookingdurs_prepost.png'), 
       device='png', width=2.75, height=1.5, units='in', scale=2.5)
```

```{r r2-g-durs-prepost-lookingprops}

g_prelookingprop_df <- g_fin %>% 
  mutate(window = '"Pre-Naming" Window',
         looking_prop = pre_looking_sum_ms/pre_dur_ms,
         median = median(looking_prop),
         mean = mean(looking_prop)) %>%
  dplyr::select("subject_id", "window", "looking_prop", "median", "mean")

G_PRE_MIN_PROP <- min(g_prelookingprop_df$looking_prop)
G_PRE_MAX_PROP <- max(g_prelookingprop_df$looking_prop)
G_PRE_MEAN_PROP <- mean(g_prelookingprop_df$looking_prop)
G_PRE_MEDIAN_PROP <- median(g_prelookingprop_df$looking_prop)

g_postlookingprop_df <- g_fin %>% 
  mutate(window = '"Post-Naming"/Analysis Window',
         looking_prop = post1_looking_sum_ms/post1_dur_ms,
         median = median(looking_prop),
         mean = mean(looking_prop)) %>%
  dplyr::select("subject_id", "window", "looking_prop", "median", "mean")

G_POST_MIN_PROP <- min(g_postlookingprop_df$looking_prop)
G_POST_MAX_PROP <- max(g_postlookingprop_df$looking_prop)
G_POST_MEAN_PROP <- mean(g_postlookingprop_df$looking_prop)
G_POST_MEDIAN_PROP <- median(g_postlookingprop_df$looking_prop)

g_prepost_lookingprop_df <- rbind(g_prelookingprop_df, g_postlookingprop_df)
g_prepost_lookingprop_df$window <- 
  factor(g_prepost_lookingprop_df$window, levels=c(
    '"Pre-Naming" Window','"Post-Naming"/Analysis Window'), ordered=T) 

g_prepost_lookingprop_label_df <- g_prepost_lookingprop_df %>%
  group_by(window) %>%
  summarize(median=median(median),
            label=paste("Median =", round(median, 2), sep=" "))

ggplot(g_prepost_lookingprop_df, aes(x=looking_prop)) +
  geom_histogram(fill="#7bccc4") +
  sb.density.theme +
  geom_vline(aes(xintercept=median), color="red", lty=2) +
  xlim(0,1) +
  ylim(0,22) +
  xlab("Looking Time Proportion") +
  ylab("Number of Trials") + 
  theme(axis.title = element_text(colour="gray30", size=11),
        axis.text = element_text(colour="gray30", size=11),
        axis.ticks = element_line(colour="gray30"),
        plot.background = element_blank(),
        strip.text.x = element_text(colour="gray30", size=11))+
  facet_wrap(~window) +
  geom_text(data=g_prepost_lookingprop_label_df,
            aes(x=median-.24, label=label), y=21, 
            color="red", size=4)

ggsave(here('supplement/plots/exp_2/pdfs', 'g_lookingprops_prepost.pdf'), 
       device='pdf', width=2.75, height=1.5, units='in', scale=2.5)
ggsave(here('supplement/plots/exp_2/pngs', 'g_lookingprops_prepost.png'), 
       device='png', width=2.75, height=1.5, units='in', scale=2.5)
```

Trials in Experiment 2 were $`r G_MEAN_TRIAL_DUR_S`$\textit{s} [$`r G_CIL_TRIAL_DUR_S`$, $`r G_CIH_TRIAL_DUR_S`$] long on average (\textit{range}: $`r G_MIN_TRIAL_DUR_S`-`r G_MAX_TRIAL_DUR_S`$\textit{s}, \textit{Med}$=`r G_MED_TRIAL_DUR_S`$\textit{s}), and infants spent an average of $`r G_MEAN_TRIAL_LOOKING_S`$\textit{s} [$`r G_CIL_TRIAL_LOOKING_S`$, $`r G_CIH_TRIAL_LOOKING_S`$] total looking at the displays (\textit{range}: $`r G_MIN_TRIAL_LOOKING_S`-`r G_MAX_TRIAL_LOOKING_S`$\textit{s}, \textit{Med}$=`r G_MED_TRIAL_LOOKING_S`$\textit{s}, or between $`r G_MIN_LOOKING_PROP`$ and $`r G_MAX_LOOKING_PROP`$ of the total trial duration;  $M=`r G_MEAN_LOOKING_PROP`$ [$`r G_CIL_LOOKING_PROP`$, $`r G_CIH_LOOKING_PROP`$], \textit{Med}$=`r G_MED_LOOKING_PROP`$).

The pre-naming window was between $`r G_MIN_PRE_DUR_S`$ and $`r G_MAX_PRE_DUR_S`$\textit{s} ($M_\textnormal{pre}=`r G_MEAN_PRE_DUR_S`$\textit{s}, $Med_\textnormal{pre}=`r G_MED_PRE_DUR_S`$\textit{s}). 

The children in our final sample spent similar proportions of time looking at the displays during the pre- and post-naming periods (pre-naming: $`r G_PRE_MIN_PROP`-`r G_PRE_MAX_PROP`$, $M_\textnormal{proportion}=`r G_PRE_MEAN_PROP`$, $Med_\textnormal{proportion}=`r G_PRE_MEDIAN_PROP`$; post-naming: $`r G_POST_MIN_PROP`-`r G_POST_MAX_PROP`$, $M_\textnormal{proportion}=`r G_POST_MEAN_PROP`$, $Med_\textnormal{proportion}=`r G_POST_MEDIAN_PROP`$). 